The Journey from Wild to Textbook Data: A Case Study from the National Longitudinal Survey of Youth

### 2021-09-16 paper/paper-jsdse/paper-jsdse.tex
messing with figures in the cleaning section

{\centering \includegraphics[width=0.7\linewidth]{figures/sample-plot-1}

@@

\caption{Getting a glimpse of the data: random sample of 36 individuals, divided into  twelve subplots. Wages are shown against year. There is a lot of variability in wages.}\label{fig:sample-plot}
\end{figure}

@@

{\centering \includegraphics[width=0.7\linewidth]{figures/feature-plot-1}

@@

\caption{Several plots showing anomalies observed the input data. XX Add a couple more plots that reveal the initial problems in the data. Plot A portrays the pattern of mean hourly wage of high school cohort from 1979 to 2018 of each ID in US Dollar; Plot B shows the distribution of their minimum, median, and maximum value. We can see that some IDs had an extremely high of wages and it made the distribution of the three features is extremely skewed.}\label{fig:feature-plot}
\end{figure}

@@

{\centering \includegraphics[width=0.7\linewidth]{figures/compare-plot-1}

@@

{\centering \includegraphics[width=0.7\linewidth]{figures/comppict-1}

@@

\caption{The distribution of the mean hourly wage after the extreme values are replaced. Plot A portrays the pattern of mean hourly wage of high school cohort from 1979 to 2018 of each ID in US Dollar; Plot B shows the distribution of their minimum, median, and maximum value transformed to log10 scale. We can see that some observations still had reasonbaly higher wages than the others. Also, some IDs' have a minimum wages that is higher than others' maximum wages.}\label{fig:comppict}
\end{figure}

@@

{\centering \includegraphics[width=0.7\linewidth]{figures/flow-chart-1}

@@

{\centering \includegraphics[width=0.7\linewidth]{figures/slope-nobs-plot-1}

@@

{\centering \includegraphics[width=0.7\linewidth]{figures/slope-gender-1}

@@

{\centering \includegraphics[width=0.7\linewidth]{figures/slope-educ-1}

>>>>

{\centering \includegraphics[width=1\linewidth]{figures/sample-plot-1}

@@

\caption{A glimpse of the refreshed data. Longitudinal profiles of wages from 1979-2018 are shown for a random sample of 36 individuals, divided into twelve subplots. Most individuals here experienced increasing wages over time, although there is considerable fluctuation from one year to another.}\label{fig:sample-plot}
\end{figure}

@@

{\centering \includegraphics[width=432px]{figures/feature-plot-1}

@@

\caption{Summary plots to check the cleaned data reveal more cleaning is necessary: longitudinal profiles of wages for all individuals 1979-2018 (A), boxplots of minimum, median, and maximum wages of each individual (B), and one individual with an unusual wage relative to their years of data (C). Some values of hourly wages are unbelievable, and some individuals have extemely unusual wages in some years.}\label{fig:feature-plot}
\end{figure}

@@

{\centering \includegraphics[width=432px]{figures/compare-plot-1}

@@

{\centering \includegraphics[width=432px]{figures/fixed-feature-plot-1}

@@

\caption{Re-make of the summary plots of the fully processed data suggest that the data is now in a reasonable state: longitudinal profiles of wages for all individuals 1979-2018 (A), boxplots of minimum, median, and maximum wages of each individual (B), and one individual with an unusual wage relative to their years of data (C). }\label{fig:fixed-feature-plot}
\end{figure}

@@

{\centering \includegraphics[width=468px]{figures/flow-chart-1}

@@

{\centering \includegraphics[width=468px]{figures/slope-nobs-plot-1}

@@

{\centering \includegraphics[width=468px]{figures/slope-gender-1}

@@

{\centering \includegraphics[width=468px]{figures/slope-educ-1}

### 2021-09-16 paper/paper.Rmd
messing with figures in the cleaning section

```{r sample-plot, echo = FALSE, fig.cap="Getting a glimpse of the data: random sample of 36 individuals, divided into  twelve subplots. Wages are shown against year. There is a lot of variability in wages.", fig.height=4, fig.width=5}
```

@@

```{r feature-plot, fig.cap = "Several plots showing anomalies observed the input data. XX Add a couple more plots that reveal the initial problems in the data. Plot A portrays the pattern of mean hourly wage of high school cohort from 1979 to 2018 of each ID in US Dollar; Plot B shows the distribution of their minimum, median, and maximum value. We can see that some IDs had an extremely high of wages and it made the distribution of the three features is extremely skewed.", fig.width=6, fig.height=4}
```

@@

```{r high-wages, fig.cap= "6 out of 45 IDs with extremely high mean hourly wage. Most of the IDs only have one point of high wage."}
```

@@

```{r compare-plot, fig.cap="Comparison between the original and the treated mean hourly wage. The orange line portray the original value of mean hourly wage, while the turquoise line display the mean hourly wages value after the extreme values imputed with the robust linear model's prediction value. We can see that some extreme spikes has been reduced by the model.", fig.height=5, fig.width=6}
```

@@

```{r comppict, fig.cap = "The distribution of the mean hourly wage after the extreme values are replaced. Plot A portrays the pattern of mean hourly wage of high school cohort from 1979 to 2018 of each ID in US Dollar; Plot B shows the distribution of their minimum, median, and maximum value transformed to log10 scale. We can see that some observations still had reasonbaly higher wages than the others. Also, some IDs' have a minimum wages that is higher than others' maximum wages.", fig.width=6, fig.height=4}
```

>>>>

```{r sample-plot, echo = FALSE, fig.cap="A glimpse of the refreshed data. Longitudinal profiles of wages from 1979-2018 are shown for a random sample of 36 individuals, divided into twelve subplots. Most individuals here experienced increasing wages over time, although there is considerable fluctuation from one year to another.", fig.height=4, fig.width=5, out.width="100%"}
```

@@

```{r feature-plot, fig.cap = "Summary plots to check the cleaned data reveal more cleaning is necessary: longitudinal profiles of wages for all individuals 1979-2018 (A), boxplots of minimum, median, and maximum wages of each individual (B), and one individual with an unusual wage relative to their years of data (C). Some values of hourly wages are unbelievable, and some individuals have extemely unusual wages in some years.", fig.width=6, fig.height=2}
```

@@

```{r high-wages, fig.cap= "6 out of 45 IDs with extremely high mean hourly wage. Most of the IDs only have one point of high wage.", eval=FALSE}
```

@@

```{r compare-plot, fig.cap="Comparison between the original and the treated mean hourly wage. The orange line portray the original value of mean hourly wage, while the turquoise line display the mean hourly wages value after the extreme values imputed with the robust linear model's prediction value. We can see that some extreme spikes has been reduced by the model.", fig.height=5, fig.width=6, outwidth="100%"}
```

@@

```{r comppict, fig.cap = "The distribution of the mean hourly wage after the extreme values are replaced. Plot A portrays the pattern of mean hourly wage of high school cohort from 1979 to 2018 of each ID in US Dollar; Plot B shows the distribution of their minimum, median, and maximum value transformed to log10 scale. We can see that some observations still had reasonbaly higher wages than the others. Also, some IDs' have a minimum wages that is higher than others' maximum wages.", fig.width=6, fig.height=4, eval=FALSE}
```

```{r fixed-feature-plot, fig.cap = "Re-make of the summary plots of the fully processed data suggest that the data is now in a reasonable state: longitudinal profiles of wages for all individuals 1979-2018 (A), boxplots of minimum, median, and maximum wages of each individual (B), and one individual with an unusual wage relative to their years of data (C). ", fig.width=6, fig.height=2}
```
